Toward single particle reconstruction without particle picking: Breaking the detection limit

### 2018-06-05 TEX/draft4.tex
Worked on caption of Fig 4 -- now need to get started on the discussion

In the second experiment, three 1D signals, each of length $L = 21$, appear at random locations in one long 1D signal, which we call a micrograph by analogy. Any two occurrences are separated by at least 20 entries. The signals appear respectively about 30, 20 and 10 million times in a micrograph of length 12.3 billion. The micrograph is then contaminated with additive white Gaussian noise. Neither the number of occurrences nor the noise level $\sigma$ are known. In the methods section, we show how autocorrelations of the micrograph can be used to estimate weighted averages of the autocorrelations of the target signals. The individual signals and their relative densities are then estimated from autocorrelations up to order three by solving a nonlinear least-squares problem.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{heterogeneous_progressive_n12300000000_466300}
	\caption{An experiment for estimate three one-dimensional signals simultaneously with noise level $\sigma=3$. Red signals are the ground truth (targets) and the blue signals are our estimations. Individual RMSE of the estimates: $0.0239393 / 0.208925 / 0.0335956$. The estimated $\gamma$'s are $0.02574 / 0.01693 / 0.00818$ and the true ones $0.02561 / 0.01707 / 0.00853$. The $\SNR$ is $1/12$. \TODO{1. to replace with a ``progress'' plot 2. replace the triangle signal 3. add error progress figure}}
	\label{fig:1Dheterosignals}
\end{figure}

>>>>

In the second experiment, three 1D signals, each of length $L = 21$, appear at random locations in one long 1D signal, which we call a micrograph by analogy. Any two occurrences are separated by at least 20 entries. The signals appear respectively about 30, 20 and 10 million times in a micrograph of length 12.3 billion. The micrograph is then contaminated with additive white Gaussian noise. This results in an $\SNR$ of about $1/9$, while about 10\% of the micrograph contains signal. Neither the number of occurrences nor the noise level $\sigma$ are known.

In the methods section, we detail how autocorrelations of the micrograph can be used to estimate weighted averages of the autocorrelations of the target signals. The individual signals and their relative densities are then estimated from autocorrelations up to order three by solving a nonlinear least-squares problem.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{heterogeneous_progressive_n12300000000_466300}
	\caption{For the second experiment, each row shows, three times, one of the target signals (red), overlaid with an estimate (blue) obtained from a growing portion of the noisy micrograph (about $10^8$, $10^9$ and $10^{10}$ entries available to compute autocorrelations.) The last column depicts evolution of the relative root mean square error in estimating each individual target signal. Signals 1 to 3 appear respectively about 30, 20 and 10 million times. With the whole micrograph available, the algorithm estimated those to be 29.8, 21.9 and 10.0 million, respectively.
%		
%		An experiment for estimate three one-dimensional signals simultaneously with noise level $\sigma=3$. Red signals are the ground truth (targets) and the blue signals are our estimations. Individual RMSE of the estimates: $0.0239393 / 0.208925 / 0.0335956$. The estimated $\gamma$'s are $0.02574 / 0.01693 / 0.00818$ and the true ones $0.02561 / 0.01707 / 0.00853$. The $\SNR$ is $1/12$. \TODO{1. to replace with a ``progress'' plot 2. replace the triangle signal 3. add error progress figure}
	}
	\label{fig:1Dheterosignals}
\end{figure}
